---
title: "hw5"
author: "Sofia Styrina"
date: "18 March 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### 1.1
```{r}

library(tidyverse)
library(GGally)
library(ca)

chairs <- read.csv('https://raw.githubusercontent.com/phuuda/2018_hse_data_analysis/master/hw5_CA_MCA/hw5_chairs.csv')

MCA <- MASS::mca(chairs[, 4:19])
MCA

geom.text.size = 3

chairs <- cbind(chairs, MCA$rs)
variables <- as_data_frame(MCA$cs)
variables$var_names <- rownames(MCA$cs)
chairs %>% 
  ggplot(aes(`1`, `2`))+
  geom_point(aes(color = Category))+
  stat_ellipse(aes(color = Category))+
  geom_text(data = variables, aes(`1`, `2`, label = var_names), size=geom.text.size)+
  theme(axis.text = element_text(colour="black"))+
  scale_x_continuous(limits = c(-0.015, 0.02))

```

### 1.2
Sessel:
* material: fabric, leather, soft padding (upholstery)
* deep seat depth, has arms & a high back, can recline
* can't roll around, rotate (swivel), or collapse (fold for storage)
* primarily for adults
* used for relaxing (& even sleeping)

Stuhl:
* material: wood, metal, paper(?), rattan, not soft
* normal seat depth, no arms, normal, back/seat depth/height are adjustable
* can roll & rotate (swivel), doesn't recline or rock, is collapsable
* for adults & children
* used for working, eating (at a table), and outdoors

Variables:
* Age adult don't weigh in as much
* SaveSpace, MaterialSeat Polyamide overlaps as well
* Rock, AddFunctions, Recline, Function, Seat.Depth, Seat.Height, MaterialSeat are some of the more decisive factors

### 2.1
```{r}
colors <- read.csv('https://raw.githubusercontent.com/phuuda/2018_hse_data_analysis/master/hw5_CA_MCA/hw5_colreg.csv')
color_names <- c("c01", "c02", "c03", "c04", "c05", "c06", "c07", "c08", "c09", "c10", "c11")
rownames(colors) <- color_names

ca <- ca(colors)
ca
summary(ca)

colors_col <- data.frame(ca$colcoord)
colors_col$rows <- rownames(ca$colcoord)

colors_row <- data.frame(ca$rowcoord)
colors_row$rows <- rownames(ca$rowcoord)

colors_col %>% 
  ggplot(aes(Dim1, Dim2, label = rows))+
  geom_text(color = "blue")+
  geom_text(data = colors_row, color = "red")+
  theme_bw()+
  labs(x = "Dim1 (42.1%)",
       y = "Dim2 (32.6%)")
```
### 2.2
Which colors are more typical to find in each genre?

* Fiction: 2, 3, 7, 8, 11, and 4
* Press: 5, 6, 9
* Spoken: 1, 10
* Academic: only 10